Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-04-27 CSM_poster/main.tex
convert final model results to bulleted list

As a whole, the final model was significant with a partial likelihood ratio of 1265.29 (p-value \textless0.0001). Its $R^2$ statistic was 0.15, and Somers' \textit{Dxy} was 0.27.

Predictors found to be significant in the final model include: device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, and whether or not the question's title ends in a question mark.

>>>>

\underline{Final model statistics}

\textcolor{dblue!70}{\ding{228}} PLR $=$ 1265.29 (p-value \textless0.0001)

\textcolor{dblue!70}{\ding{228}} $R^2 =$ 0.15

\textcolor{dblue!70}{\ding{228}} Somers' \textit{Dxy} $=$ 0.27

\underline{Significant Predictors} Device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, whether or not the question's title ends in a question mark.
